Coupling PDEs on XD-YD domains with Lagrange multipliers

### 2019-05-07 stab/stab.tex
done

  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 2) {\pgfuseplotmark{*}};  
  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Two different settings considered for the Babu{\v s}ka problem
    \eqref{eq:bab}. Trace mesh (on $\Gamma_L$) of $\Omega_h$ equals (left)
    or differs (right) from $\Gamma_H$.
  }
\label{fig:domains}
\end{figure}

@@

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
on the inverse of the bilinear 
\[
\langle (-\Delta_{00})^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space used piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p0_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
  \end{aligned}
\end{equation}
%
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

@@

\begin{minipage}{0.47\textwidth}
  \begin{equation}\label{eq:coupled}
    \begin{aligned}
      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
      u^i &= g^i &\mbox{ on }\Gamma^i_D\partial\Omega^{i}\setminus\Gamma,\\
      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
      -\Delta \hat{u} - \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
      \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
      u - \hat{u} &= h&\mbox{ on }\Gamma.\\
    \end{aligned}
\end{equation}
\null
\par\xdef\tpd{\the\prevdepth}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
  \begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
  \draw[black!60!white, very thick] (0,0) rectangle (4, 4);
  \draw[black!60!white, very thick] (2, 0) rectangle (2, 4);

@@

  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Different mesh settings considered for the coupled problem
    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
    non-conforming (from left to right).
  }
\label{fig:multi_domains}
\end{figure}
%
In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
consists only of the existing facets of the mesh. In the conforming setting 
we consider matching and non-matching cases as defined above. Let us also
remark that the approximation of the space $\hat{V}$ shall always be constructed
on the multiplier mesh $\Gamma_H$.

\subsubscection{P1-P1-P1 discretization with $\Gamma$ conformity}

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 8.8E-1(--)   & 2.0E0(--)    & 8.9E-1(--)   & 20 & 8.0 & 8.6E-1(--)   & 6.7E-1(--)   & 1.7E-1(--)   & 23 & 4.5  \\
4.4E-2 & 4.4E-1(1.01) & 1.0E0(0.99)  & 2.1E-1(2.10) & 22 & 8.4 & 4.4E-1(0.99) & 3.4E-1(1.00) & 4.5E-2(1.89) & 25 & 4.5  \\
2.2E-2 & 2.2E-1(1.00) & 5.0E-1(1.00) & 5.1E-2(2.03) & 22 & 8.5 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.2E-2(1.95) & 25 & 4.6  \\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.3E-2(2.01) & 21 & 8.6 & 1.1E-1(1.00) & 8.4E-2(1.00) & 3.0E-3(1.98) & 24 & 4.7  \\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 3.2E-3(2.00) & 21 & 8.7 & 5.5E-2(1.00) & 4.2E-2(1.00) & 7.5E-4(1.99) & 24 & 4.7  \\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 7.9E-4(2.00) & 21 & 8.7 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.9E-4(1.99) & 22 & 4.7  \\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 2.0E-4(2.00) & 21 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 4.7E-5(2.00) & 22 & --   \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P1 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p1}
  \end{center}
\end{table}

@@

\subsubscection{P1-P1-P0 discretization with $\Gamma$ conformity}

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 9.3E-1(--)   & 2.0E0(--)    & 2.9E0(--)    & 21 & 4.5 & 8.6E-1(--)   & 6.7E-1(--)   & 9.2E-1(--)   & 29 & 7.8\\
4.4E-2 & 4.4E-1(1.06) & 1.0E0(0.99)  & 1.1E0(1.43)  & 28 & 4.8 & 4.4E-1(0.99) & 3.4E-1(1.00) & 3.4E-1(1.42) & 31 & 8.1\\
2.2E-2 & 2.2E-1(1.02) & 5.0E-1(1.00) & 4.1E-1(1.39) & 28 & 5.0 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.4E-1(1.34) & 32 & 8.3\\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.7E-1(1.28) & 27 & 5.1 & 1.1E-1(1.00) & 8.4E-2(1.00) & 5.6E-2(1.26) & 30 & 8.4\\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 7.5E-2(1.19) & 27 & 5.2 & 5.5E-2(1.00) & 4.2E-2(1.00) & 2.5E-2(1.18) & 30 & 8.5\\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 3.5E-2(1.11) & 27 & 5.2 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.1E-2(1.11) & 29 & 8.5\\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 1.7E-2(1.07) & 27 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 5.5E-3(1.06) & 29 & -- \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P0 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p0}
  \end{center}
\end{table}

@@

\subsubscection{Non-conforming setting}

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.3E-2 & 1.3E0(--)    & 7.0E-1(--)   & 1.2E0(--)    & 28 & 5.2 & 1.3E0(--)    & 7.0E-1(--)   & 1.7E0(--)     & 31 & 8.6\\   
4.3E-2 & 8.1E-1(0.68) & 3.5E-1(1.04) & 6.4E-1(0.95) & 29 & 5.6 & 8.1E-1(0.68) & 3.5E-1(1.04) & 7.6E-1(1.18)  & 34 & 9.3\\ 
2.2E-2 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.3E-1(0.99) & 29 & 5.8 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.6E-1(1.10)  & 34 & 9.7\\ 
1.1E-2 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.6E-1(1.00) & 27 & 6.0 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.8E-1(1.05)  & 34 & 9.9\\ 
5.5E-3 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.3E-2(1.00) & 27 & 6.0 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.7E-2(1.03)  & 33 & 10.0\\
2.8E-3 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.1E-2(1.00) & 26 & 6.1 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.3E-2(1.01)  & 32 & 10.0\\
1.4E-3 & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.00) & 26 & --  & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.01)  & 31 & 10.0\\
    \hline
  \end{tabular}
    }
    \caption{Non-conforming setting. Approximation errors, number of preconditioner MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P1 (left) and P1-P1-P0 (right) elements.}
  \label{tab:coupled_non}
  \end{center}
\end{table}

>>>>

  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 1) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0.5, 2) {\pgfuseplotmark{*}};  
  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Matching (left) and non-mathching (right) setting considered
    for the Babu{\v s}ka problem.}
\label{fig:domains}
\end{figure}

@@

MinRes iteration counts with the Riesz map preconditioner are shown in
Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
on the inverse of the bilinear form
\[
\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
\]
%

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p1}
  \end{center}
\end{table}
%
Concerning approximation properties of the discretization, note that the error
for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
that the multiplier in the manufactured test case does not satisfy the
Dirichlet boundary conditions employed in the discrete problem.

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
for the space $V$ while the multiplier space uses piecewise constants elements
(P0). In both the matching and non-matching case the discretization is unstable
and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
%
\begin{equation}\label{eq:p0_stab}
\begin{aligned}
&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
  \end{aligned}
\end{equation}
%
where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.

@@

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
  \label{tab:p1_p0}
  \end{center}
\end{table}

@@

\begin{minipage}{0.47\textwidth}
  \begin{equation}\label{eq:coupled}
    \begin{aligned}
      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
      u^i &= g^i &\mbox{ on }\Gamma^i_D=\partial\Omega^{i}\setminus\Gamma,\\
      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
      -\Delta \hat{u} - \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
      \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
      u - \hat{u} &= h&\mbox{ on }\Gamma.\\
    \end{aligned}
\end{equation}
\null
\par\xdef\tpd{\the\prevdepth}
\end{minipage}
\hfill
\begin{minipage}{0.47\textwidth}
  \begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
  \draw[black!60!white, very thick] (0,0) rectangle (4, 4);
  \draw[black!60!white, very thick] (2, 0) rectangle (2, 4);

@@

  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
\end{tikzpicture}
%
\end{center}
  \caption{Different mesh settings considered for the coupled problem
    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
    non-conforming (from left to right).
  }
\label{fig:multi_domains}
\end{figure}
%
In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
consists only of the existing facets of the mesh. In the conforming setting 
we consider matching and non-matching cases as defined above. We remark
that the approximation of the space $\hat{V}$ shall always be constructed
on the multiplier mesh $\Gamma_H$.

\subsection{P1-P1-P1 discretization with $\Gamma$ conformity}
Let us first consider a conforming setting and an approximation of all
the spaces involved in \eqref{eq:coupled_weak} in terms of P1 elements.
As with the Babu{\v s}ka problem \eqref{eq:bab} the discrete multiplier
space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_H$. In fact,
the boundary conditions are necessary to obtain an invertible linear system.

Table \ref{tab:coupled_p1_p1} summarizes the results for both matching
and non-matching tessilations. In the latter case, a stabilization term
\cite{burman2009interior} is added similar to \eqref{eq:p1_stab} (we set $\gamma=1$).
In both cases the results show evidence of the inf-sup stability of the
discretization. We note that the $L^2$ error of the multiplier converges
quadratically; in contrast to the test problem in \eqref{eq:bab} the solution
here \emph{does} satisfy $p=0$ on $\partial\Gamma$.

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 8.8E-1(--)   & 2.0E0(--)    & 8.9E-1(--)   & 20 & 8.0 & 8.6E-1(--)   & 6.7E-1(--)   & 1.7E-1(--)   & 23 & 4.5  \\
4.4E-2 & 4.4E-1(1.01) & 1.0E0(0.99)  & 2.1E-1(2.10) & 22 & 8.4 & 4.4E-1(0.99) & 3.4E-1(1.00) & 4.5E-2(1.89) & 25 & 4.5  \\
2.2E-2 & 2.2E-1(1.00) & 5.0E-1(1.00) & 5.1E-2(2.03) & 22 & 8.5 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.2E-2(1.95) & 25 & 4.6  \\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.3E-2(2.01) & 21 & 8.6 & 1.1E-1(1.00) & 8.4E-2(1.00) & 3.0E-3(1.98) & 24 & 4.7  \\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 3.2E-3(2.00) & 21 & 8.7 & 5.5E-2(1.00) & 4.2E-2(1.00) & 7.5E-4(1.99) & 24 & 4.7  \\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 7.9E-4(2.00) & 21 & 8.7 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.9E-4(1.99) & 22 & 4.7  \\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 2.0E-4(2.00) & 21 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 4.7E-5(2.00) & 22 & --   \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P1 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p1}
  \end{center}
\end{table}

@@

\subsection{P1-P1-P0 discretization with $\Gamma$ conformity} 
We shall next have the multiplier space be spanned by piecewise constant
functions. Following \eqref{eq:bab} a stabilization \cite{burman2014projection}
is employed in both the matching and non-matching cases. Table \ref{tab:coupled_p1_p0}
confirms that the discretization is inf-sup stable.

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.8E-2 & 9.3E-1(--)   & 2.0E0(--)    & 2.9E0(--)    & 21 & 4.5 & 8.6E-1(--)   & 6.7E-1(--)   & 9.2E-1(--)   & 29 & 7.8\\
4.4E-2 & 4.4E-1(1.06) & 1.0E0(0.99)  & 1.1E0(1.43)  & 28 & 4.8 & 4.4E-1(0.99) & 3.4E-1(1.00) & 3.4E-1(1.42) & 31 & 8.1\\
2.2E-2 & 2.2E-1(1.02) & 5.0E-1(1.00) & 4.1E-1(1.39) & 28 & 5.0 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.4E-1(1.34) & 32 & 8.3\\
1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.7E-1(1.28) & 27 & 5.1 & 1.1E-1(1.00) & 8.4E-2(1.00) & 5.6E-2(1.26) & 30 & 8.4\\
5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 7.5E-2(1.19) & 27 & 5.2 & 5.5E-2(1.00) & 4.2E-2(1.00) & 2.5E-2(1.18) & 30 & 8.5\\
2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 3.5E-2(1.11) & 27 & 5.2 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.1E-2(1.11) & 29 & 8.5\\
1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 1.7E-2(1.07) & 27 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 5.5E-3(1.06) & 29 & -- \\
    \hline
  \end{tabular}
    }
    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P0 elements. Conforming (left) matching and (right) non-matching case.}
  \label{tab:coupled_p1_p0}
  \end{center}
\end{table}

@@

\subsection{Non-conforming setting}
Finally a non-conforming setting is considered with P1-P1-P1 and P1-P1-P0
discretizations. In both cases stabilization terms are employed to obtain
inf-sup stability, cf. Table \ref{tab:coupled_non}. Note that compared to the
conforming case the multiplier convergence with P1 elements is only linear.
The order from the conforming case is preserved with P0 elements. Note also
that with both elements $u_h$ converges with order $\tfrac{1}{2}$; the approximation
struggles to capture the kink of the solution which now occurs within the finite element
cells.

\begin{table}
  \begin{center}
    \scriptsize{
  \begin{tabular}{c|ccc|c|c||ccc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
    \hline
8.3E-2 & 1.3E0(--)    & 7.0E-1(--)   & 1.2E0(--)    & 28 & 5.2 & 1.3E0(--)    & 7.0E-1(--)   & 1.7E0(--)     & 31 & 8.6\\   
4.3E-2 & 8.1E-1(0.68) & 3.5E-1(1.04) & 6.4E-1(0.95) & 29 & 5.6 & 8.1E-1(0.68) & 3.5E-1(1.04) & 7.6E-1(1.18)  & 34 & 9.3\\ 
2.2E-2 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.3E-1(0.99) & 29 & 5.8 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.6E-1(1.10)  & 34 & 9.7\\ 
1.1E-2 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.6E-1(1.00) & 27 & 6.0 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.8E-1(1.05)  & 34 & 9.9\\ 
5.5E-3 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.3E-2(1.00) & 27 & 6.0 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.7E-2(1.03)  & 33 & 10.0\\
2.8E-3 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.1E-2(1.00) & 26 & 6.1 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.3E-2(1.01)  & 32 & 10.0\\
1.4E-3 & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.00) & 26 & --  & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.01)  & 31 & 10.0\\
    \hline
  \end{tabular}
    }
    \caption{Non-conforming setting. Approximation errors, number of preconditioned MinRes iterations ($n$) and
      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
      with P1-P1-P1 (left) and P1-P1-P0 (right) elements.}
  \label{tab:coupled_non}
  \end{center}
\end{table}
